---
title: "Sets for handwriterRF"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sets-for-handwriterRF}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(handwriterSetBuilder)
```

## Preparing the Data

### CSAFE Prompt Data

1.  Get cluster fill rates
    1.  Load cluster assignments from RDS file
    2.  handwriter::get_cluster_fill_rates()
2.  Get writer ID, prompt, session, and rep from docname (internal helpers)
3.  Make master data frame of cluster fill rates with added columns for writer ID, prompt, session, and rep
4. Save as csafe_prompt_cfr data object

### CVL Prompt Data

1.  Get cluster fill rates
    1.  Load cluster assignments from RDS file
    2.  handwriter::get_cluster_fill_rates()
2.  Get writer ID and prompt from docname (internal helpers)
3.  Make master data frame of cluster fill rates with added columns for writer ID and prompt
4. Save as cvl_prompt_cfr data object

### CVL Line Data

1.  Get cluster fill rates
    1.  Load cluster assignments from RDS file
    2.  handwriter::get_cluster_fill_rates()
2.  Get writer ID, prompt, and line from docname (internal helpers)
3.  Make master data frame of cluster fill rates with added columns for writer ID, prompt, and line
4. Save as cvl_line_cfc data object

## Building Sets

### CSAFE Prompt Data

1.  **CSAFE Training Set**
    1.  Select i writers
    2.  Short prompts - randomly select 2 PHR from each writer
    3.  Long prompts - randomly select 1 LND and 1 WOZ from each writer
2.  **CSAFE Validation Set**
    1.  Select i writers
    2.  Short prompts - randomly select 2 PHR from each writer
    3.  Long prompts - randomly select 1 LND and 1 WOZ from each writer
3.  **CSAFE Test Set**
    1.  Select i writers
    2.  Short prompts - randomly select 2 PHR from each writer
    3.  Long prompts - randomly select 1 LND and 1 WOZ from each writer

### CVL Prompt and Line Data

1.  **CVL Training Set**
    1.  Select r writers (but not the 27 writers who wrote prompts 7 and 8)
    2.  Drop the German language prompts
    3.  Randomly pick 4 prompts
        1.  Short prompts - randomly pick x lines from the first 2 selected prompts
        2.  Long prompts - use the remaining 2 selected prompts
2.  **CVL Validation Set**
    1.  Select s writers (but not the 27 writers who wrote prompts 7 and 8)
    2.  Drop the German language prompts
    3.  Randomly pick 4 prompts
        1.  Short prompts - randomly pick x lines from the first 2 selected prompts
        2.  Long prompts - use the remaining 2 selected prompts
3.  **CVL Test Set**
    1.  Select the remaining writers, including the 27 writers who wrote prompts 7 and 8
    2.  Drop the German language prompts
    3.  Randomly pick 4 prompts
        1.  Short prompts - randomly pick x lines from the first 2 selected prompts
        2.  Long prompts - use the remaining 2 selected prompts
